```{r}
df <- read.csv('HR_comma_sep.csv')
str(df)

```

```{r}
library('ggplot2')
ggplot(aes(x=satisfaction_level, y = last_evaluation), data = df)+
  geom_point(alpha = 1/20)+
  scale_x_continuous(breaks = seq(0,1,0.05))+
  scale_y_continuous(breaks = seq(0,1,0.05))
  
  
```
Too many people not satisfied with jobs but still working at high level just for the money.
```{r}
library('ggplot2')
ggplot(aes(x=satisfaction_level, y = last_evaluation, color = salary), data = df)+
  geom_point(alpha = 1/5)

```
Found a special spot

```{r}
ggplot(aes(x=satisfaction_level, y = last_evaluation, color = left.bucket), data = df)+
  geom_point(alpha = 1/5)

```


```{r}
library('dplyr')
df_special <- subset(df, satisfaction_level < 0.125 & last_evaluation > 0.75)
df_special <- df_special %>% group_by(sales) %>% mutate(count = n())
df_special$sales <- factor(df_special$sales, levels = c('sales', 'technical', 'support','IT','accounting','hr','product_mng','marketing','RandD','managment'))

ggplot(aes(sales), data = df_special)+
  geom_bar(aes(fill = salary))+
  coord_flip()+
  title(main = 'unsatisfied_employees')
```
Where do these unsatisfied employees work?
```{r}
df_special$average_monthly_hour.bucket <- cut(df_special$average_montly_hours, breaks = seq(130,310,30))
library('graphics')
ggplot(aes(sales), data = df_special)+
  geom_bar(aes(fill = average_monthly_hour.bucket))+
  coord_flip()+
  title(main = 'unsatisfied_employees')
  
  

```
How much do they earn?
```{r}
df$time_spend_company.bucket <- as.factor(df$time_spend_company)
df$number_project.bucket <- as.factor(df$number_project)
df$left.bucket <- as.factor(df$left)
df$satisfaction_level.bucket <- cut(df$satisfaction_level, breaks = seq(0,1,0.1))
df$last_evaluation.bucket <- cut(df$last_evaluation, breaks = seq(0,1,0.1))
```
adding some column
```{r}
ggplot(aes(x=time_spend_company.bucket, y= average_montly_hours), data = df)+
  geom_boxplot()

```
How much time has a person spend vs. his working hours.

```{r}
df_special$time_spend_company.bucket <- as.factor(df_special$time_spend_company)
ggplot(aes(x=time_spend_company.bucket, y= average_montly_hours), data = df_special)+
  geom_boxplot()

```
How much time has a person spend vs. his working hours? special category.
```{r}
ggplot(aes(x=average_montly_hours, y=last_evaluation), data = df)+
  geom_point(alpha = 1/10)

```
average_montly_hours vs. last_evaluation

```{r}
ggplot(aes(x=average_montly_hours, y=satisfaction_level), data = df)+
  geom_point(alpha = 1/10)
```
average_montly_hours vs. satisfaction_level
conclude:- Some employees are exploited.

```{r}
ggplot(aes(x=time_spend_company.bucket, y=satisfaction_level), data = df)+
  geom_boxplot()

```
time_spend_company vs. satisfaction_level
```{r}
ggplot(aes(x=time_spend_company.bucket, y=last_evaluation), data = df)+
  geom_boxplot()

```
time_spent_company vs evaluation. Checking whether stay in the company affects evaluation

```{r}
ggplot(aes(x=number_project.bucket, y= average_montly_hours), data =df)+
  geom_boxplot()
```
checking whether no. of projects affect average_montly_hours
```{r}
ggplot(aes(x=number_project.bucket, y= satisfaction_level), data =df)+
  geom_boxplot()

```
checking weather number of projects effects satisfaction level.
```{r}
ggplot(aes(x=sales, y = average_montly_hours), data =df)+
  geom_violin(fill = 'pink')
```
How much work does a person do in each  category?
```{r}
sales_summary <- df %>% group_by(sales) %>%
  summarise(mean.satisfation_level = mean(satisfaction_level),
            mean.last_evaluation = mean(last_evaluation),
            median.average_montly_hours = median(average_montly_hours),
            mean.time_spend_company = mean(time_spend_company),
            mean.left = mean(left),
            n = n()) %>% 
  arrange(sales)
```
created a dataset grouped by sales.
```{r}
satisfation_summary <- df %>% group_by(satisfaction_level.bucket) %>%
  summarise(mean.satisfation_level = mean(satisfaction_level),
            mean.last_evaluation = mean(last_evaluation),
            median.average_montly_hours = median(average_montly_hours),
            mean.time_spend_company = mean(time_spend_company),
            mean.left = mean(left),
            n = n()) %>% 
  arrange(satisfaction_level.bucket)

```
```{r}
evaluation_summary <- df %>% group_by(last_evaluation.bucket) %>%
  summarise(mean.satisfation_level = mean(satisfaction_level),
            mean.last_evaluation = mean(last_evaluation),
            median.average_montly_hours = median(average_montly_hours),
            mean.time_spend_company = mean(time_spend_company),
            mean.left = mean(left),
            n = n()) %>% 
  arrange(last_evaluation.bucket)
```
```{r}
salary_summary <- df %>% group_by(salary) %>%
  summarise(mean.satisfation_level = mean(satisfaction_level),
            mean.last_evaluation = mean(last_evaluation),
            median.average_montly_hours = median(average_montly_hours),
            mean.time_spend_company = mean(time_spend_company),
            mean.left = mean(left),
            n = n()) %>% 
  arrange(salary)

```
```{r}


```


